### 2019-09-24 papers/journal/problem.tex
Update on connectedness property

\item {\em Universal condition}:
  if there is a connectedness property that is satisfied by each valid VTS.
\item{\em synthesis on incomplete VTS}:
    Given an incomplete VTS, if we can predict missing parts.
\end{enumerate}
The goal is to find the minimum graph connectivity properties for each of the condition. We will present two encodings for the existential condition and one each for the universal condition and synthesis.
% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions. 
\subsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a $k$-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and the specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%

The implementation of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
%
So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
%
Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
% Used E as edge and L_e L_n as label for node and the edge,

>>>>

\item {\em Universal condition}:
  if there is a connectedness property that is satisfied by each valid VTS.
\item{\em Synthesis on incomplete VTS}:
    given an incomplete VTS, if we can predict missing parts.
\end{enumerate}
The goal is to find the minimum graph connectivity properties for each of the condition. We will present two encodings for the existential condition and one each for the universal condition and synthesis.
% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions. 
\subsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a $k$-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and the specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%

The implementation of the $k$-connectedness property is challenging as it requires reasoning about each combination of $k - 1$ edge removal. 
%
%The implementation of the k-connectedness property is challenging as it requires reasoning about every possible k − 1 edge removals.
%
So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected, i.e., search for a $k$ edge removal that disconnects the graph.
%
Note that this suffices to find the exact $k$, as we are starting from the smallest value of $k$ and subsequently incrementing it by one.
%Note that this suffice to find the correct $k$ as we are starting from smallest $k$ ($k = 1$) and subsequently increment it by one.     
% Used E as edge and L_e L_n as label for node and the edge,
